---
title: "Goalie Card Builder"
author: '@DraftLook'
date: "21/05/2021"
output: html_fragment
params:
  name: Jesper Wallstedt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r, echo=FALSE}
library(tidyverse)
library(rio)
library(eeptools)
library(janitor)
library(sjmisc)

name <- "Jesper Wallstedt"

url <- "https://docs.google.com/spreadsheets/d/1gsGn70hHh80nC5cOJHc3TMHNEqWg4UawKXtPcuSK2Hw/edit#gid=1081527217"
data <- rio::import(file = url,which = 2)
data <- clean_names(data)

player_data <- subset(data, player_name== params$name)

```

<style type="text/css">

@import url('https://fonts.googleapis.com/css2?family=Spectral&display=swap');

.playerheader {
font-size: 150%;
}
.body {
font-size: 110%;
margin-left: 23.25%;
}
table { 
width: 100%;
margin-top: -9%;
background-color: white !important;
}
table, th, td {
border: 1px solid black;
border-collapse: collapse;
}
.header {
font-size: 110%;
padding: 2%;
text-align: center;
}
.num {
text-align: center;
font-size: 150%;
padding: 2%;
}
.footer {
text-align: center;
border-top-style: hidden;
}
.biotext{
width: 32.5%;
margin-left: 22.5%;
padding: 0%;
}
.image {
float: left;
width: 18%;
height: 10%;
margin-top: 4.75%;
margin-left: 0%;
}
.tableclass{
float: right;
width: 42.5%;
margin-top: 10%;
}
.break {
border-top-style: solid;
border-top-color: black;
margin-left: 0px;
width: 100%;
padding: 0%;
}
.bio{
margin-left: 0%;
padding: 0%;
}
.bodytext {
margin-left: 22.5%;
}
.row { display: flex; padding-bottom: 1%; margin-left: 22.5%; margin-right: 0.05%; font-size: 110% }
.column { flex: 0 0 50%; align-self: center; }
.tab{
font-size: 110%;
}
.prftext{
font-family: Spectral, sans serif;
margin-left: 22.5%;
}
thead, tfoot, tr:nth-child(even) { 
background: white;
}
.playercard {
font-family: Lucida Console, monospace;
width: 129%;
margin-left: -29%;
}

</style>

<div class = "playercard">
<!-- Building Table -->
<div class = "tableclass">
  <table>
    <tr class="header">
      <th>**GAMES**</th>
      <th>**SAVE %**</th>
      <th>**GAA**</th>
    </tr>
    <tr>
      <td class="num">`r player_data$games_played`</td>
      <td class="num">.908</td>
      <td class="num">2.23</td>
    </tr>
  </table>
</div>

<!-- Inserting Image -->
<div class="image">
```{r pressure, echo=FALSE, out.width = "100%", out.height = "90%", out.extra = 'style="padding-left: 10%; padding-right: 10%"' }
knitr::include_graphics(player_data$logo_url)
```
</div>

<div class="biotext">
  <h1 class="bio">`r toupper(player_data$player_name)`<h1>
  <hr class="break" style="margin-top: -5%;"></hr>
  <h4 class = "bio" style="margin-top: -5%">`r toupper(player_data$position)`<h4>
  <h4 class ="bio" style="margin-top: -4%">`r toupper(paste(player_data$team, paste("(",player_data$league,")", sep = ""), sep = " "))`<h4>
  <h5 class="bio" style="margin-top: -4%">SELLING POINT -- `r toupper(player_data$selling_point)`<h5>
  <h5 class="bio" style="margin-top: -4%">HEIGHT/WEIGHT -- `r paste(player_data$height, paste(player_data$weight, "LBS", sep = " "), sep = "/")`<h5>
  <h5 class="bio" style="margin-top: -4%">BIRTHDATE -- `r gsub("-", "/", player_data$birthdate)`<h5>
  <h5 class="bio" style="margin-top: -4%">AGE -- `r paste(round(player_data$age,2), "YEARS", sep = " ")`<h5>
  </div>

<div class="bodytext">
  <br>
  <p class="tab" style="margin-top: -1.5%;"> `r player_data$description`<p>
  <p class="tab"> Similar To: `r player_data$similar_to`<p>
  <hr class="break" style="border:1px solid black"> </hr>
  <p class ="tab"> **Positives:** <p>
  <p class = "tab"> `r if(!is_empty(player_data$strength_1)) {paste("•", player_data$strength_1, sep = " ")}`<p>
  <p class = "tab"> `r if(!is_empty(player_data$strength_2)) {paste("•", player_data$strength_2, sep = " ")}`<p>
  <p class = "tab"> `r if(!is_empty(player_data$strength_3)) {paste("•", player_data$strength_3, sep = " ")}`<p>
  <p class = "tab"> `r if(!is_empty(player_data$strength_4)) {paste("•", player_data$strength_4, sep = " ")}`<p>
  <p class = "tab"> `r if(!is_empty(player_data$strength_5)) {paste("•", player_data$strength_5, sep = " ")}`<p>
  <p class = "tab"> `r if(!is_empty(player_data$strength_6)) {paste("•", player_data$strength_6, sep = " ")}`<p>
  <p class = "tab"> `r if(!is_empty(player_data$strength_7)) {paste("•", player_data$strength_7, sep = " ")}`<p>
  <p class = "tab"> `r if(!is_empty(player_data$strength_8)) {paste("•", player_data$strength_8, sep = " ")}`<p>
  <p class = "tab"> `r if(!is_empty(player_data$strength_9)) {paste("•", player_data$strength_9, sep = " ")}`<p>
  <p class = "tab"> `r if(!is_empty(player_data$strength_10)) {paste("•", player_data$strength_10, sep = " ")}`<p>

  <p class="tab"> **Negatives:** <p>
  <p class = "tab"> `r if(!is_empty(player_data$weakness_1)) {paste("•", player_data$weakness_1, sep = " ")}`<p>
  <p class = "tab"> `r if(!is_empty(player_data$weakness_2)) {paste("•", player_data$weakness_2, sep = " ")}`<p>
  <p class = "tab"> `r if(!is_empty(player_data$weakness_3)) {paste("•", player_data$weakness_3, sep = " ")}`<p>
  <p class = "tab"> `r if(!is_empty(player_data$weakness_4)) {paste("•", player_data$weakness_4, sep = " ")}`<p>
  <p class = "tab"> `r if(!is_empty(player_data$weakness_5)) {paste("•", player_data$weakness_5, sep = " ")}`<p>
  <p class = "tab"> `r if(!is_empty(player_data$weakness_6)) {paste("•", player_data$weakness_6, sep = " ")}`<p>
  <p class = "tab"> `r if(!is_empty(player_data$weakness_7)) {paste("•", player_data$weakness_7, sep = " ")}`<p>
  <p class = "tab"> `r if(!is_empty(player_data$weakness_8)) {paste("•", player_data$weakness_8, sep = " ")}`<p>
  <p class = "tab"> `r if(!is_empty(player_data$weakness_9)) {paste("•", player_data$weakness_9, sep = " ")}`<p>
  <p class = "tab"> `r if(!is_empty(player_data$weakness_10)) {paste("•", player_data$weakness_10, sep = " ")}`<p>

  <hr class="break" style="border:1px solid black"> </hr>
  <p class="tab"> **20-80 SCOUTING GRADES:** <p>
</div>

<div class="row">
  <div class="column"> ATHLETICISM -- `r player_data$athleticism_grade`</div>
  <div class="column"> REFLEXES -- `r player_data$reflexes_grade`</div>
</div>
<div class="row">
  <div class="column"> POSITIONING -- `r player_data$positioning_grade`</div>
  <div class="column"> RECOVERY -- `r player_data$recovery_grade`</div>
</div>
</div>