---
title: NHL Draft Rankings Preview
author: '@DraftLook'
date: '2021-05-23'
slug: preview
categories:
  - Rankings
tags: []
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(knitr.duplicate.label = "allow")
```

```{r echo=FALSE}
library(tidyverse)
library(rio)
library(eeptools)
library(janitor)
library(sjmisc)
library(linguisticsdown)

url <- "https://docs.google.com/spreadsheets/d/15LQi8UZ41jR6bq6MLIGyjRSagLMigFaDl0hgeH2UpWc/edit?usp=sharing"
info <- rio::import(file = url,which = 2)
info <- clean_names(info)
```

<style type="text/css">

@import url('https://fonts.googleapis.com/css2?family=Spectral&display=swap');

.playerheader {
font-size: 150%;
}
.body {
font-size: 110%;
margin-left: 23.25%;
}
table { 
width: 100%;
margin-top: -4%;
background-color: white !important;
}
table, th, td {
border: 1px solid black;
border-collapse: collapse;
}
.header {
font-size: 110%;
padding: 2%;
text-align: center;
}
.num {
text-align: center;
font-size: 150%;
padding: 2%;
}
.footer {
text-align: center;
border-top-style: hidden;
}
.biotext{
width: 32.5%;
margin-left: 22.5%;
}
.image {
float: left;
width: 20%;
height: 10%;
margin-top: 4.75%;
margin-left: 2.5%;
}
.tableclass{
float: right;
width: 42.5%;
margin-top: 6%;
}
.break {
border-top-style: solid;
border-top-color: black;
margin-left: 0px;
width: 100%;
padding: 0%;
}
.bio{
margin-left: 0%;
padding: 2.5%;
}
.bodytext {
margin-left: 22.5%;
}
.row { display: flex; padding-bottom: 1%; margin-left: 22.5%; margin-right: 0.05%; font-size: 110% }
.column { flex: 0 0 50%; align-self: center; }
.tab{
font-size: 110%;
}
.full{
width: 129%;
margin-left: -29.25%;
}
.prftext{
font-family: Spectral, sans serif;
margin-left: 22.5%;
}
thead, tfoot, tr:nth-child(even) { 
background: white;
}
.playercard {
font-family: Lucida Console, monospace;
}

</style>

<div class="full">
<!-- PLAYER CARD-->
<div class="playercard">
```{r, echo=FALSE}
library(tidyverse)
library(rio)
library(eeptools)
library(janitor)
library(sjmisc)

name <- "Luke Hughes"

url <- "https://docs.google.com/spreadsheets/d/1gsGn70hHh80nC5cOJHc3TMHNEqWg4UawKXtPcuSK2Hw/edit#gid=478681110"
data <- rio::import(file = url,which = 2)
data <- clean_names(data)
data$league_multiplier <- as.numeric(data$league_multiplier)

player_data <- subset(data, player_name == "Sasha Pastujov")

```

<!-- Building Table -->
<div class = "tableclass">
<table>
<tr class="header">
<th>**GOALS**</th>
<th>**ASSISTS**</th>
<th>**POINTS**</th>
</tr>
<tr>
<td class="num">`r round(player_data$goals/player_data$games_played,2)`</td>
<td class="num">`r round(player_data$assists/player_data$games_played,2)`</td>
<td class="num">`r round(player_data$points/player_data$games_played,2)`</td>
</tr>
<tr>
<td class="footer">PER GAME</td>
<td class="footer">PER GAME</td>
<td class="footer">PER GAME</td>
</tr>
<tr class="header">
<td>**ADJ GOALS**</td>
<td>**ADJ ASSISTS**</td>
<td>**ADJ POINTS**</td>
</tr>
<tr>
<td class="num">
`r if((player_data$goals/player_data$games_played*player_data$league_multiplier*82.0)<10) { formatC((player_data$goals/player_data$games_played*player_data$league_multiplier*82.0),digits=2, format="f")} else {formatC((player_data$goals/player_data$games_played*player_data$league_multiplier*82.0),digits=1, format="f")}`
</td>
<td class="num">
`r if((player_data$assists/player_data$games_played*player_data$league_multiplier*82.0)<10) { formatC((player_data$assists/player_data$games_played*player_data$league_multiplier*82.0),digits=2, format="f")} else {formatC((player_data$assists/player_data$games_played*player_data$league_multiplier*82.0),digits=1, format="f")}`
</td>
<td class="num">
`r if((player_data$points/player_data$games_played*player_data$league_multiplier*82.0)<10) { formatC((player_data$points/player_data$games_played*player_data$league_multiplier*82.0),digits=2, format="f")} else {formatC((player_data$points/player_data$games_played*player_data$league_multiplier*82.0),digits=1, format="f")}`
</td>
</tr>
<tr>
<td class="footer">PER 82</td>
<td class="footer">PER 82</td>
<td class="footer">PER 82</td>
</tr>
</table>
</div>

<!-- Inserting Image -->
<div class="image">
```{r pressure, echo=FALSE, out.width = "75%", out.extra = 'style="padding-left: 10%; padding-right: 10%"' }
knitr::include_graphics(player_data$logo_url)
```
</div>

<div class="biotext">
<h1 class="bio" style="margin-top: 2.5%;">`r toupper(player_data$player_name)`<h1>
<hr class="break" style="margin-top: -6%;"></hr>
<h4 class = "bio" style="margin-top: -7%">`r toupper(player_data$position)`<h4>
<h4 class ="bio" style="margin-top: -9.5%">`r toupper(paste(player_data$team, paste("(",player_data$league,")", sep = ""), sep = " "))`<h4>
<br>
<h4 class="bio" style="margin-top: -15.5%">SELLING POINT -- `r toupper(player_data$selling_point)`<h4>
<h4 class="bio" style="margin-top: -10.5%">HEIGHT/WEIGHT -- `r paste(player_data$height, paste(player_data$weight, "LBS", sep = " "), sep = "/")`<h4>
<h4 class="bio" style="margin-top: -10.5%">BIRTHDATE -- `r gsub("-", "/", player_data$birthdate)`<h4>
<h4 class="bio" style="margin-top: -10.5%">AGE -- `r paste(round(player_data$age,2), "YEARS", sep = " ")`<h4>
</div>

<div class="bodytext">
<br>
<p class="tab" style="margin-top: -1.5%;"> `r player_data$description`<p>
<p class="tab"> **Similar To:** `r player_data$similar_to`<p>
<hr class="break" style="border:1px solid black"> </hr>
<p class ="tab"> **Positives:** <p>
<p class = "tab"> `r if(!is_empty(player_data$strength_1)) {paste("•", player_data$strength_1, sep = " ")}`<p>
<p class = "tab"> `r if(!is_empty(player_data$strength_2)) {paste("•", player_data$strength_2, sep = " ")}`<p>
<p class = "tab"> `r if(!is_empty(player_data$strength_3)) {paste("•", player_data$strength_3, sep = " ")}`<p>
<p class = "tab"> `r if(!is_empty(player_data$strength_4)) {paste("•", player_data$strength_4, sep = " ")}`<p>
<p class = "tab"> `r if(!is_empty(player_data$strength_5)) {paste("•", player_data$strength_5, sep = " ")}`<p>
<p class = "tab"> `r if(!is_empty(player_data$strength_6)) {paste("•", player_data$strength_6, sep = " ")}`<p>
<p class = "tab"> `r if(!is_empty(player_data$strength_7)) {paste("•", player_data$strength_7, sep = " ")}`<p>
<p class = "tab"> `r if(!is_empty(player_data$strength_8)) {paste("•", player_data$strength_8, sep = " ")}`<p>
<p class = "tab"> `r if(!is_empty(player_data$strength_9)) {paste("•", player_data$strength_9, sep = " ")}`<p>
<p class = "tab"> `r if(!is_empty(player_data$strength_10)) {paste("•", player_data$strength_10, sep = " ")}`<p>

<p class="tab"> **Negatives:** <p>
<p class = "tab"> `r if(!is_empty(player_data$weakness_1)) {paste("•", player_data$weakness_1, sep = " ")}`<p>
<p class = "tab"> `r if(!is_empty(player_data$weakness_2)) {paste("•", player_data$weakness_2, sep = " ")}`<p>
<p class = "tab"> `r if(!is_empty(player_data$weakness_3)) {paste("•", player_data$weakness_3, sep = " ")}`<p>
<p class = "tab"> `r if(!is_empty(player_data$weakness_4)) {paste("•", player_data$weakness_4, sep = " ")}`<p>
<p class = "tab"> `r if(!is_empty(player_data$weakness_5)) {paste("•", player_data$weakness_5, sep = " ")}`<p>
<p class = "tab"> `r if(!is_empty(player_data$weakness_6)) {paste("•", player_data$weakness_6, sep = " ")}`<p>
<p class = "tab"> `r if(!is_empty(player_data$weakness_7)) {paste("•", player_data$weakness_7, sep = " ")}`<p>
<p class = "tab"> `r if(!is_empty(player_data$weakness_8)) {paste("•", player_data$weakness_8, sep = " ")}`<p>
<p class = "tab"> `r if(!is_empty(player_data$weakness_9)) {paste("•", player_data$weakness_9, sep = " ")}`<p>
<p class = "tab"> `r if(!is_empty(player_data$weakness_10)) {paste("•", player_data$weakness_10, sep = " ")}`<p>

<hr class="break" style="border:1px solid black"> </hr>
<p class="tab"> **20-80 SCOUTING GRADES:** <p>
</div>

<div class="row">
<div class="column"> SKATING -- `r player_data$skating_grade`</div>
<div class="column"> PLAYMAKING -- `r player_data$playmaking_grade`</div>
</div>
<div class="row">
<div class="column"> PUCK SKILLS -- `r player_data$puck_skills_grade`</div>
<div class="column"> SCORING -- `r player_data$scoring_grade`</div>
</div>
<div class="row">
<div class="column"> HOCKEY IQ -- `r player_data$hockey_iq_grade`</div>
<div class="column"> PHYSICALITY -- `r player_data$physicality`</div>
</div>
</div>

<div class="prftext">
<!-- One Thing I Love -->
<hr class="break" style="border:1px solid black"> </hr>
**One Thing I Love**: `r if(!is_empty(info$otil_text_1)) {info$otil_text_1}`
`r if(!is_empty(info$otil_text_1)) { "<br>" }`
```{r}
if(!is_empty(info$otil_clip_1)) {knitr::include_graphics(info$otil_clip_1)}
```
`r if(!is_empty(info$otil_clip_1)) { "<br>" }`
`r if(!is_empty(info$otil_text_2)) {info$otil_text_2}`
`r if(!is_empty(info$otil_text_2)) { "<br>" }`
```{r}
if(!is_empty(info$otil_clip_2)) {knitr::include_graphics(info$otil_clip_2)}
```
`r if(!is_empty(info$otil_clip_2)) { "<br>" }`
`r if(!is_empty(info$otil_text_3)) {info$otil_text_3}`
`r if(!is_empty(info$otil_text_3)) { "<br>" }`
```{r}
if(!is_empty(info$otil_clip_3)) {knitr::include_graphics(info$otil_clip_3)}
```
`r if(!is_empty(info$otil_clip_3)) { "<br>" }`
`r if(!is_empty(info$otil_text_4)) {info$otil_text_4}`
`r if(!is_empty(info$otil_text_4)) { "<br>" }`
```{r}
if(!is_empty(info$otil_clip_4)) {knitr::include_graphics(info$otil_clip_4)}
```
`r if(!is_empty(info$otil_clip_4)) { "<br>" }`
`r if(!is_empty(info$otil_text_5)) {info$otil_text_5}`
`r if(!is_empty(info$otil_text_5)) { "<br>" }`
```{r}
if(!is_empty(info$otil_clip_5)) {knitr::include_graphics(info$otil_clip_5)}
```
`r if(!is_empty(info$otil_clip_5)) { "<br>" }`

<!-- Another Thing I Love -->
`r if(!is_empty(info$atil_text_1)) {paste("**Another Thing I Love:**", info$atil_text_1, sep=" ")}`
`r if(!is_empty(info$atil_text_1)) { "<br>" }`
```{r}
if(!is_empty(info$atil_clip_1)) {knitr::include_graphics(info$atil_clip_1)}
```
`r if(!is_empty(info$atil_clip_1)) { "<br>" }`
`r if(!is_empty(info$atil_text_2)) {info$atil_text_2}`
`r if(!is_empty(info$atil_text_2)) { "<br>" }`
```{r}
if(!is_empty(info$atil_clip_2)) {knitr::include_graphics(info$atil_clip_2)}
```
`r if(!is_empty(info$atil_clip_2)) { "<br>" }`
`r if(!is_empty(info$atil_text_3)) {info$atil_text_3}`
`r if(!is_empty(info$atil_text_3)) { "<br>" }`
```{r}
if(!is_empty(info$atil_clip_3)) {knitr::include_graphics(info$atil_clip_3)}
```
`r if(!is_empty(info$atil_clip_3)) { "<br>" }`
`r if(!is_empty(info$atil_text_4)) {info$atil_text_4}`
`r if(!is_empty(info$atil_text_4)) { "<br>" }`
```{r}
if(!is_empty(info$atil_clip_4)) {knitr::include_graphics(info$atil_clip_4)}
```
`r if(!is_empty(info$atil_clip_4)) { "<br>" }`
`r if(!is_empty(info$atil_text_5)) {info$atil_text_5}`
`r if(!is_empty(info$atil_text_5)) { "<br>" }`
```{r}
if(!is_empty(info$atil_clip_5)) {knitr::include_graphics(info$atil_clip_5)}
```
`r if(!is_empty(info$atil_clip_5)) { "<br>" }`

<!-- Swing Skill -->
`r if(!is_empty(info$omtil_text_1)) {paste("**Swing Skill:**", info$ss_text_1, sep=" ")}`
`r if(!is_empty(info$ss_text_1)) { "<br>" }`
```{r}
if(!is_empty(info$ss_clip_1)) {knitr::include_graphics(info$ss_clip_1)}
```
`r if(!is_empty(info$ss_clip_1)) { "<br>" }`
`r if(!is_empty(info$ss_text_2)) {info$ss_text_2}`
`r if(!is_empty(info$ss_text_2)) { "<br>" }`
```{r}
if(!is_empty(info$ss_clip_2)) {knitr::include_graphics(info$ss_clip_2)}
```
`r if(!is_empty(info$ss_clip_2)) { "<br>" }`
`r if(!is_empty(info$ss_text_3)) {info$ss_text_3}`
`r if(!is_empty(info$ss_text_3)) { "<br>" }`
```{r}
if(!is_empty(info$ss_clip_3)) {knitr::include_graphics(info$ss_clip_3)}
```
`r if(!is_empty(info$ss_clip_3)) { "<br>" }`
`r if(!is_empty(info$ss_text_4)) {info$ss_text_4}`
`r if(!is_empty(info$ss_text_4)) { "<br>" }`
```{r}
if(!is_empty(info$ss_clip_4)) {knitr::include_graphics(info$ss_clip_4)}
```
`r if(!is_empty(info$ss_clip_4)) { "<br>" }`
`r if(!is_empty(info$ss_text_5)) {info$ss_text_5}`
`r if(!is_empty(info$ss_text_5)) { "<br>" }`
```{r}
if(!is_empty(info$ss_clip_5)) {knitr::include_graphics(info$ss_clip_5)}
```
`r if(!is_empty(info$ss_clip_5)) { "<br>" }`
`r if(!is_empty(info$ss_text_6)) {info$ss_text_6}`
`r if(!is_empty(info$ss_text_6)) { "<br>" }`
```{r}
if(!is_empty(info$ss_clip_6)) {knitr::include_graphics(info$ss_clip_6)}
```
`r if(!is_empty(info$ss_clip_6)) { "<br>" }`
`r if(!is_empty(info$ss_text_7)) {info$ss_text_7}`
`r if(!is_empty(info$ss_text_7)) { "<br>" }`
```{r}
if(!is_empty(info$ss_clip_7)) {knitr::include_graphics(info$ss_clip_7)}
```
`r if(!is_empty(info$ss_clip_7)) { "<br>" }`
`r if(!is_empty(info$ss_text_8)) {info$ss_text_8}`
`r if(!is_empty(info$ss_text_8)) { "<br>" }`
```{r}
if(!is_empty(info$ss_clip_8)) {knitr::include_graphics(info$ss_clip_8)}
```
`r if(!is_empty(info$ss_clip_8)) { "<br>" }`
`r if(!is_empty(info$ss_text_9)) {info$ss_text_9}`
`r if(!is_empty(info$ss_text_9)) { "<br>" }`
```{r}
if(!is_empty(info$ss_clip_9)) {knitr::include_graphics(info$ss_clip_9)}
```
`r if(!is_empty(info$ss_clip_9)) { "<br>" }`
`r if(!is_empty(info$ss_text_10)) {info$ss_text_10}`
`r if(!is_empty(info$ss_text_10)) { "<br>" }`
```{r}
if(!is_empty(info$ss_clip_10)) {knitr::include_graphics(info$ss_clip_10)}
```
`r if(!is_empty(info$ss_clip_10)) { "<br>" }`


<!-- Development -->
`r if(!is_empty(info$dev_text_1)) {paste("**Development:**", info$dev_text_1, sep=" ")}`
`r if(!is_empty(info$dev_text_1)) { "<br>" }`
```{r}
if(!is_empty(info$dev_clip_1)) {knitr::include_graphics(info$dev_clip_1)}
```
`r if(!is_empty(info$dev_clip_1)) { "<br>" }`
`r if(!is_empty(info$dev_text_2)) {info$dev_text_2}`
`r if(!is_empty(info$dev_text_2)) { "<br>" }`
```{r}
if(!is_empty(info$dev_clip_2)) {knitr::include_graphics(info$dev_clip_2)}
```
`r if(!is_empty(info$dev_clip_2)) { "<br>" }`
`r if(!is_empty(info$dev_text_3)) {info$dev_text_3}`
`r if(!is_empty(info$dev_text_3)) { "<br>" }`
```{r}
if(!is_empty(info$dev_clip_3)) {knitr::include_graphics(info$dev_clip_3)}
```
`r if(!is_empty(info$dev_clip_3)) { "<br>" }`
`r if(!is_empty(info$dev_text_4)) {info$dev_text_4}`
`r if(!is_empty(info$dev_text_4)) { "<br>" }`
```{r}
if(!is_empty(info$dev_clip_4)) {knitr::include_graphics(info$dev_clip_4)}
```
`r if(!is_empty(info$dev_clip_4)) { "<br>" }`
`r if(!is_empty(info$dev_text_5)) {info$dev_text_5}`
`r if(!is_empty(info$dev_text_5)) { "<br>" }`
```{r}
if(!is_empty(info$dev_clip_5)) {knitr::include_graphics(info$dev_clip_5)}
```
`r if(!is_empty(info$dev_clip_5)) { "<br>" }`

<!-- Projection -->
**Projection:**
<br>
`r if(!is_empty(info$top_end_proj)) {paste("*Top-end:*", info$top_end_proj, sep=" ")}`
<br>
`r if(!is_empty(info$mid_level_proj)) {paste("*Mid-level:*", info$mid_level_proj, sep=" ")}`
<br>
`r if(!is_empty(info$low_end_proj)) {paste("*Low-end:*", info$low_end_proj, sep=" ")}`
</div>

</div>